%---------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,fleqn,oneside,openany]{book} 
\input{structure}
\usepackage{booktabs}
\usepackage{pdflscape}
\usepackage{float}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage[document]{ragged2e}
\begin{document}
\input{journal_macros}

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------
\thispagestyle{empty}
{\Huge Large Synoptic Survey Telescope} 
\linebreak 
\linebreak 
{\Huge Galaxies Science Roadmap}
\linebreak
\linebreak
{\centering
\input{authorlist}
}
\vfill

%----------------------------------------------------------------------------------------
%	COPYRIGHT PAGE
%----------------------------------------------------------------------------------------
\newpage
\thispagestyle{empty}

\noindent
{\justify
The {\it Large Synoptic Survey Telescope Galaxies Science Roadmap} represents the collective efforts of more than one hundred scientists to define the critical research activities to prepare our field to maximize
the science return of the LSST dataset. We want to thank the LSST Corporation for their
support in developing this Roadmap and for supporting LSST-related science more broadly.
We also wish to thank the LSST Galaxies Science Collaboration members for their efforts
over the years in developing the case for extragalactic science with LSST. 
}
\vspace{1in}

Inquiries about this report or its content can be addressed to Brant Robertson ({\tt brant@ucsc.edu}) and the LSST Galaxies Science Collaboration ({\tt lsst-galaxies@lsstcorp.org}).
\vspace{1in}
\input{VersionDate}


%----------------------------------------------------------------------------------------
% Abstract
%----------------------------------------------------------------------------------------

\include{abstract}

%----------------------------------------------------------------------------------------
% Table of Contents
%----------------------------------------------------------------------------------------

\tableofcontents % Print the table of contents 


%----------------------------------------------------------------------------------------
%	Chapters
%----------------------------------------------------------------------------------------

\input{introduction}
\input{science_background}
\input{task_lists}

%---------------------------------------------------------------------------------------
% References
%---------------------------------------------------------------------------------------

\begin{thebibliography}{87}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Abraham} {et~al.}(1994){Abraham}, {Valdes}, {Yee}, \& {van den
  Bergh}}]{abraham1994a}
{Abraham}, R.~G., {Valdes}, F., {Yee}, H.~K.~C., \& {van den Bergh}, S. 1994,
  \apj, 432, 75

\bibitem[{{Abraham} {et~al.}(2003){Abraham}, {van den Bergh}, \&
  {Nair}}]{abraham2003a}
{Abraham}, R.~G., {van den Bergh}, S., \& {Nair}, P. 2003, \apj, 588, 218

\bibitem[{{Abraham} \& {van Dokkum}(2014)}]{abraham2014a}
{Abraham}, R.~G., \& {van Dokkum}, P.~G. 2014, \pasp, 126, 55

\bibitem[{{Applegate} {et~al.}(2014){Applegate}, {von der Linden}, {Kelly},
  {Allen}, {Allen}, {Burchat}, {Burke}, {Ebeling}, {Mantz}, \&
  {Morris}}]{applegate2014a}
{Applegate}, D.~E., {et~al.} 2014, \mnras, 439, 48

\bibitem[{{Atkinson} {et~al.}(2013){Atkinson}, {Abraham}, \&
  {Ferguson}}]{atkinson2013}
{Atkinson}, A.~M., {Abraham}, R.~G., \& {Ferguson}, A.~M.~N. 2013, \apj, 765,
  28

\bibitem[{{Awan} {et~al.}(2016){Awan}, {Gawiser}, {Kurczynski}, {Jones},
  {Zhan}, {Padilla}, {Mu{\~n}oz Arancibia}, {Orsi}, {Cora}, \&
  {Yoachim}}]{awan2016a}
{Awan}, H., {et~al.} 2016, \apj, 829, 50

\bibitem[{{Baldry} {et~al.}(2006){Baldry}, {Balogh}, {Bower}, {Glazebrook},
  {Nichol}, {Bamford}, \& {Budavari}}]{baldry2006a}
{Baldry}, I.~K., {Balogh}, M.~L., {Bower}, R.~G., {Glazebrook}, K., {Nichol},
  R.~C., {Bamford}, S.~P., \& {Budavari}, T. 2006, \mnras, 373, 469

\bibitem[{{Bellagamba} {et~al.}(2017){Bellagamba}, {Roncarelli}, {Maturi}, \&
  {Moscardini}}]{bellagamba2017a}
{Bellagamba}, F., {Roncarelli}, M., {Maturi}, M., \& {Moscardini}, L. 2017,
  ArXiv e-prints

\bibitem[{{Bowler} {et~al.}(2017){Bowler}, {Dunlop}, {McLure}, \&
  {McLeod}}]{bowler2017a}
{Bowler}, R.~A.~A., {Dunlop}, J.~S., {McLure}, R.~J., \& {McLeod}, D.~J. 2017,
  \mnras, 466, 3612

\bibitem[{{Bullock} \& {Johnston}(2005)}]{bullock2005a}
{Bullock}, J.~S., \& {Johnston}, K.~V. 2005, \apj, 635, 931

\bibitem[{{Chiang} {et~al.}(2014){Chiang}, {Overzier}, \&
  {Gebhardt}}]{chiang2014a}
{Chiang}, Y.-K., {Overzier}, R., \& {Gebhardt}, K. 2014, \apjl, 782, L3

\bibitem[{{Choi} {et~al.}(2012){Choi}, {Tyson}, {Morrison}, {Jee}, {Schmidt},
  {Margoniner}, \& {Wittman}}]{choi2012a}
{Choi}, A., {Tyson}, J.~A., {Morrison}, C.~B., {Jee}, M.~J., {Schmidt}, S.~J.,
  {Margoniner}, V.~E., \& {Wittman}, D.~M. 2012, \apj, 759, 101

\bibitem[{{Conselice} {et~al.}(2003){Conselice}, {Bershady}, {Dickinson}, \&
  {Papovich}}]{conselice2003a}
{Conselice}, C.~J., {Bershady}, M.~A., {Dickinson}, M., \& {Papovich}, C. 2003,
  \aj, 126, 1183

\bibitem[{{Conselice} {et~al.}(2000){Conselice}, {Bershady}, \&
  {Jangren}}]{conselice2000a}
{Conselice}, C.~J., {Bershady}, M.~A., \& {Jangren}, A. 2000, \apj, 529, 886

\bibitem[{{Cooper} {et~al.}(2010){Cooper}, {Coil}, {Gerke}, {Newman}, {Bundy},
  {Conselice}, {Croton}, {Davis}, {Faber}, {Guhathakurta}, {Koo}, {Lin},
  {Weiner}, {Willmer}, \& {Yan}}]{cooper2010a}
{Cooper}, M.~C., {et~al.} 2010, \mnras, 409, 337

\bibitem[{{Darg} {et~al.}(2010){Darg}, {Kaviraj}, {Lintott}, {Schawinski},
  {Sarzi}, {Bamford}, {Silk}, {Andreescu}, {Murray}, {Nichol}, {Raddick},
  {Slosar}, {Szalay}, {Thomas}, \& {Vandenberg}}]{darg2010a}
{Darg}, D.~W., {et~al.} 2010, \mnras, 401, 1552

\bibitem[{{de Jong} {et~al.}(2015){de Jong}, {Verdoes Kleijn}, {Boxhoorn},
  {Buddelmeijer}, {Capaccioli}, {Getman}, {Grado}, {Helmich}, {Huang},
  {Irisarri}, {Kuijken}, {La Barbera}, {McFarland}, {Napolitano}, {Radovich},
  {Sikkema}, {Valentijn}, {Begeman}, {Brescia}, {Cavuoti}, {Choi}, {Cordes},
  {Covone}, {Dall'Ora}, {Hildebrandt}, {Longo}, {Nakajima}, {Paolillo},
  {Puddu}, {Rifatto}, {Tortora}, {van Uitert}, {Buddendiek},
  {Harnois-D{\'e}raps}, {Erben}, {Eriksen}, {Heymans}, {Hoekstra}, {Joachimi},
  {Kitching}, {Klaes}, {Koopmans}, {K{\"o}hlinger}, {Roy}, {Sif{\'o}n},
  {Schneider}, {Sutherland}, {Viola}, \& {Vriend}}]{dejong2015a}
{de Jong}, J.~T.~A., {et~al.} 2015, \aap, 582, A62

\bibitem[{{Driver} {et~al.}(2011){Driver}, {Hill}, {Kelvin}, {Robotham},
  {Liske}, {Norberg}, {Baldry}, {Bamford}, {Hopkins}, {Loveday}, {Peacock},
  {Andrae}, {Bland-Hawthorn}, {Brough}, {Brown}, {Cameron}, {Ching}, {Colless},
  {Conselice}, {Croom}, {Cross}, {de Propris}, {Dye}, {Drinkwater}, {Ellis},
  {Graham}, {Grootes}, {Gunawardhana}, {Jones}, {van Kampen}, {Maraston},
  {Nichol}, {Parkinson}, {Phillipps}, {Pimbblet}, {Popescu}, {Prescott},
  {Roseboom}, {Sadler}, {Sansom}, {Sharp}, {Smith}, {Taylor}, {Thomas},
  {Tuffs}, {Wijesinghe}, {Dunne}, {Frenk}, {Jarvis}, {Madore}, {Meyer},
  {Seibert}, {Staveley-Smith}, {Sutherland}, \& {Warren}}]{driver2011a}
{Driver}, S.~P., {et~al.} 2011, \mnras, 413, 971

\bibitem[{{Driver} {et~al.}(2009){Driver}, {Norberg}, {Baldry}, {Bamford},
  {Hopkins}, {Liske}, {Loveday}, {Peacock}, {Hill}, {Kelvin}, {Robotham},
  {Cross}, {Parkinson}, {Prescott}, {Conselice}, {Dunne}, {Brough}, {Jones},
  {Sharp}, {van Kampen}, {Oliver}, {Roseboom}, {Bland-Hawthorn}, {Croom},
  {Ellis}, {Cameron}, {Cole}, {Frenk}, {Couch}, {Alister}, {Proctor}, {De
  Propris}, {Doyle}, {Edmondson}, {Nichol}, {Thomas}, {Eales}, {Jarvis},
  {Kuijken}, {Lahav}, {Madore}, {Seibert}, {Meyer}, {Staveley-Smith},
  {Phillipps}, {Popescu}, {Sansom}, {Sutherland}, {Tuffs}, \&
  {Warren}}]{driver2009a}
---. 2009, Astronomy and Geophysics, 50, 050000

\bibitem[{{Driver} {et~al.}(2016){Driver}, {Wright}, {Andrews}, {Davies},
  {Kafle}, {Lange}, {Moffett}, {Mannering}, {Robotham}, {Vinsen}, {Alpaslan},
  {Andrae}, {Baldry}, {Bauer}, {Bamford}, {Bland-Hawthorn}, {Bourne}, {Brough},
  {Brown}, {Cluver}, {Croom}, {Colless}, {Conselice}, {da Cunha}, {De Propris},
  {Drinkwater}, {Dunne}, {Eales}, {Edge}, {Frenk}, {Graham}, {Grootes},
  {Holwerda}, {Hopkins}, {Ibar}, {van Kampen}, {Kelvin}, {Jarrett}, {Jones},
  {Lara-Lopez}, {Liske}, {Lopez-Sanchez}, {Loveday}, {Maddox}, {Madore},
  {Mahajan}, {Meyer}, {Norberg}, {Penny}, {Phillipps}, {Popescu}, {Tuffs},
  {Peacock}, {Pimbblet}, {Prescott}, {Rowlands}, {Sansom}, {Seibert}, {Smith},
  {Sutherland}, {Taylor}, {Valiante}, {Vazquez-Mata}, {Wang}, {Wilkins}, \&
  {Williams}}]{driver2016a}
---. 2016, \mnras, 455, 3911

\bibitem[{{Duffy} {et~al.}(2012){Duffy}, {Meyer}, {Staveley-Smith}, {Bernyk},
  {Croton}, {Koribalski}, {Gerstmann}, \& {Westerlund}}]{duffy2012a}
{Duffy}, A.~R., {Meyer}, M.~J., {Staveley-Smith}, L., {Bernyk}, M., {Croton},
  D.~J., {Koribalski}, B.~S., {Gerstmann}, D., \& {Westerlund}, S. 2012,
  \mnras, 426, 3385

\bibitem[{{Fern{\'a}ndez} {et~al.}(2016){Fern{\'a}ndez}, {Gim}, {van Gorkom},
  {Yun}, {Momjian}, {Popping}, {Chomiuk}, {Hess}, {Hunt}, {Kreckel}, {Lucero},
  {Maddox}, {Oosterloo}, {Pisano}, {Verheijen}, {Hales}, {Chung}, {Dodson},
  {Golap}, {Gross}, {Henning}, {Hibbard}, {Jaff{\'e}}, {Donovan Meyer},
  {Meyer}, {Sanchez-Barrantes}, {Schiminovich}, {Wicenec}, {Wilcots},
  {Bershady}, {Scoville}, {Strader}, {Tremou}, {Salinas}, \&
  {Ch{\'a}vez}}]{fernandez2016a}
{Fern{\'a}ndez}, X., {et~al.} 2016, \apjl, 824, L1

\bibitem[{{Fern{\'a}ndez} {et~al.}(2013){Fern{\'a}ndez}, {van Gorkom}, {Hess},
  {Pisano}, {Kreckel}, {Momjian}, {Popping}, {Oosterloo}, {Chomiuk},
  {Verheijen}, {Henning}, {Schiminovich}, {Bershady}, {Wilcots}, \&
  {Scoville}}]{fernandez2013a}
---. 2013, arXiv:1303.2659

\bibitem[{{Flaugher}(2005)}]{flaugher2005a}
{Flaugher}, B. 2005, International Journal of Modern Physics A, 20, 3121

\bibitem[{{Glazebrook}(2013)}]{glazebrook2013a}
{Glazebrook}, K. 2013, \pasa, 30, e056

\bibitem[{{Grogin} {et~al.}(2011){Grogin}, {Kocevski}, {Faber}, {Ferguson},
  {Koekemoer}, {Riess}, {Acquaviva}, {Alexander}, {Almaini}, {Ashby}, {Barden},
  {Bell}, {Bournaud}, {Brown}, {Caputi}, {Casertano}, {Cassata}, {Castellano},
  {Challis}, {Chary}, {Cheung}, {Cirasuolo}, {Conselice}, {Roshan Cooray},
  {Croton}, {Daddi}, {Dahlen}, {Dav{\'e}}, {de Mello}, {Dekel}, {Dickinson},
  {Dolch}, {Donley}, {Dunlop}, {Dutton}, {Elbaz}, {Fazio}, {Filippenko},
  {Finkelstein}, {Fontana}, {Gardner}, {Garnavich}, {Gawiser}, {Giavalisco},
  {Grazian}, {Guo}, {Hathi}, {H{\"a}ussler}, {Hopkins}, {Huang}, {Huang},
  {Jha}, {Kartaltepe}, {Kirshner}, {Koo}, {Lai}, {Lee}, {Li}, {Lotz}, {Lucas},
  {Madau}, {McCarthy}, {McGrath}, {McIntosh}, {McLure}, {Mobasher},
  {Moustakas}, {Mozena}, {Nandra}, {Newman}, {Niemi}, {Noeske}, {Papovich},
  {Pentericci}, {Pope}, {Primack}, {Rajan}, {Ravindranath}, {Reddy}, {Renzini},
  {Rix}, {Robaina}, {Rodney}, {Rosario}, {Rosati}, {Salimbeni}, {Scarlata},
  {Siana}, {Simard}, {Smidt}, {Somerville}, {Spinrad}, {Straughn}, {Strolger},
  {Telford}, {Teplitz}, {Trump}, {van der Wel}, {Villforth}, {Wechsler},
  {Weiner}, {Wiklind}, {Wild}, {Wilson}, {Wuyts}, {Yan}, \&
  {Yun}}]{grogin2011a}
{Grogin}, N.~A., {et~al.} 2011, \apjs, 197, 35

\bibitem[{{Heckman} {et~al.}(2005){Heckman}, {Hoopes}, {Seibert}, {Martin},
  {Salim}, {Rich}, {Kauffmann}, {Charlot}, {Barlow}, {Bianchi}, {Byun},
  {Donas}, {Forster}, {Friedman}, {Jelinsky}, {Lee}, {Madore}, {Malina},
  {Milliard}, {Morrissey}, {Neff}, {Schiminovich}, {Siegmund}, {Small},
  {Szalay}, {Welsh}, \& {Wyder}}]{heckman2005a}
{Heckman}, T.~M., {et~al.} 2005, \apjl, 619, L35

\bibitem[{{Hocking} {et~al.}(2015){Hocking}, {Geach}, {Davey}, \&
  {Sun}}]{hocking2015a}
{Hocking}, A., {Geach}, J.~E., {Davey}, N., \& {Sun}, Y. 2015,
  arXiv:arXiv150701589

\bibitem[{{Hoekstra} {et~al.}(2015){Hoekstra}, {Herbonnet}, {Muzzin}, {Babul},
  {Mahdavi}, {Viola}, \& {Cacciato}}]{hoekstra2015a}
{Hoekstra}, H., {Herbonnet}, R., {Muzzin}, A., {Babul}, A., {Mahdavi}, A.,
  {Viola}, M., \& {Cacciato}, M. 2015, \mnras, 449, 685

\bibitem[{{Holwerda} \& {Blyth}(2010)}]{holwerda2010a}
{Holwerda}, B., \& {Blyth}, S. 2010, arXiv:1007.4101

\bibitem[{{Holwerda} {et~al.}(2011){Holwerda}, {Blyth}, {Baker}, \& {MeerKAT
  Deep HI Survey Team}}]{holwerda2011a}
{Holwerda}, B.~W., {Blyth}, S., {Baker}, A.~J., \& {MeerKAT Deep HI Survey
  Team}. 2011, in Bulletin of the AAS, Vol.~43, Abstract \#217, \#433.17

\bibitem[{{Ivezic} {et~al.}(2008){Ivezic}, {Tyson}, {Abel}, {Acosta},
  {Allsman}, {AlSayyad}, {Anderson}, {Andrew}, {Angel}, {Angeli}, {Ansari},
  {Antilogus}, {Arndt}, {Astier}, {Aubourg}, {Axelrod}, {Bard}, {Barr},
  {Barrau}, {Bartlett}, {Bauman}, {Beaumont}, {Becker}, {Becla}, {Beldica},
  {Bellavia}, {Blanc}, {Blandford}, {Bloom}, {Bogart}, {Borne}, {Bosch},
  {Boutigny}, {Brandt}, {Brown}, {Bullock}, {Burchat}, {Burke}, {Cagnoli},
  {Calabrese}, {Chandrasekharan}, {Chesley}, {Cheu}, {Chiang}, {Claver},
  {Connolly}, {Cook}, {Cooray}, {Covey}, {Cribbs}, {Cui}, {Cutri}, {Daubard},
  {Daues}, {Delgado}, {Digel}, {Doherty}, {Dubois}, {Dubois-Felsmann},
  {Durech}, {Eracleous}, {Ferguson}, {Frank}, {Freemon}, {Gangler}, {Gawiser},
  {Geary}, {Gee}, {Geha}, {Gibson}, {Gilmore}, {Glanzman}, {Goodenow},
  {Gressler}, {Gris}, {Guyonnet}, {Hascall}, {Haupt}, {Hernandez}, {Hogan},
  {Huang}, {Huffer}, {Innes}, {Jacoby}, {Jain}, {Jee}, {Jernigan},
  {Jevremovic}, {Johns}, {Jones}, {Juramy-Gilles}, {Juric}, {Kahn}, {Kalirai},
  {Kallivayalil}, {Kalmbach}, {Kantor}, {Kasliwal}, {Kessler}, {Kirkby},
  {Knox}, {Kotov}, {Krabbendam}, {Krughoff}, {Kubanek}, {Kuczewski},
  {Kulkarni}, {Lambert}, {Le Guillou}, {Levine}, {Liang}, {Lim}, {Lintott},
  {Lupton}, {Mahabal}, {Marshall}, {Marshall}, {May}, {McKercher}, {Migliore},
  {Miller}, {Mills}, {Monet}, {Moniez}, {Neill}, {Nief}, {Nomerotski},
  {Nordby}, {O'Connor}, {Oliver}, {Olivier}, {Olsen}, {Ortiz}, {Owen}, {Pain},
  {Peterson}, {Petry}, {Pierfederici}, {Pietrowicz}, {Pike}, {Pinto}, {Plante},
  {Plate}, {Price}, {Prouza}, {Radeka}, {Rajagopal}, {Rasmussen}, {Regnault},
  {Ridgway}, {Ritz}, {Rosing}, {Roucelle}, {Rumore}, {Russo}, {Saha},
  {Sassolas}, {Schalk}, {Schindler}, {Schneider}, {Schumacher}, {Sebag},
  {Sembroski}, {Seppala}, {Shipsey}, {Silvestri}, {Smith}, {Smith}, {Strauss},
  {Stubbs}, {Sweeney}, {Szalay}, {Takacs}, {Thaler}, {Van Berg}, {Vanden Berk},
  {Vetter}, {Virieux}, {Xin}, {Walkowicz}, {Walter}, {Wang}, {Warner},
  {Willman}, {Wittman}, {Wolff}, {Wood-Vasey}, {Yoachim}, {Zhan}, \& {for the
  LSST Collaboration}}]{ivezic2008a}
{Ivezic}, Z., {et~al.} 2008, arXiv:0805.2366

\bibitem[{{Jarvis}(2012)}]{jarvis2012a}
{Jarvis}, M.~J. 2012, African Skies, 16, 44

\bibitem[{{Johnston} {et~al.}(2008){Johnston}, {Bullock}, {Sharma}, {Font},
  {Robertson}, \& {Leitner}}]{johnston2008a}
{Johnston}, K.~V., {Bullock}, J.~S., {Sharma}, S., {Font}, A., {Robertson},
  B.~E., \& {Leitner}, S.~N. 2008, \apj, 689, 936

\bibitem[{{Johnston} {et~al.}(2007){Johnston}, {Bailes}, {Bartel}, {Baugh},
  {Bietenholz}, {Blake}, {Braun}, {Brown}, {Chatterjee}, {Darling}, {Deller},
  {Dodson}, {Edwards}, {Ekers}, {Ellingsen}, {Feain}, {Gaensler}, {Haverkorn},
  {Hobbs}, {Hopkins}, {Jackson}, {James}, {Joncas}, {Kaspi}, {Kilborn},
  {Koribalski}, {Kothes}, {Landecker}, {Lenc}, {Lovell}, {Macquart},
  {Manchester}, {Matthews}, {McClure-Griffiths}, {Norris}, {Pen}, {Phillips},
  {Power}, {Protheroe}, {Sadler}, {Schmidt}, {Stairs}, {Staveley-Smith},
  {Stil}, {Taylor}, {Tingay}, {Tzioumis}, {Walker}, {Wall}, \&
  {Wolleben}}]{johnston2007a}
{Johnston}, S., {et~al.} 2007, \pasa, 24, 174

\bibitem[{{Kaiser} {et~al.}(2010){Kaiser}, {Burgett}, {Chambers}, {Denneau},
  {Heasley}, {Jedicke}, {Magnier}, {Morgan}, {Onaka}, \& {Tonry}}]{kaiser2010a}
{Kaiser}, N., {et~al.} 2010, in Society of Photo-Optical Instrumentation
  Engineers (SPIE) Conference Series, Vol. 7733, Society of Photo-Optical
  Instrumentation Engineers (SPIE) Conference Series, 0

\bibitem[{{Kartaltepe} {et~al.}(2007){Kartaltepe}, {Sanders}, {Scoville},
  {Calzetti}, {Capak}, {Koekemoer}, {Mobasher}, {Murayama}, {Salvato},
  {Sasaki}, \& {Taniguchi}}]{kartaltepe2007a}
{Kartaltepe}, J.~S., {et~al.} 2007, \apjs, 172, 320

\bibitem[{{Kaviraj}(2014{\natexlab{a}})}]{kaviraj2014b}
{Kaviraj}, S. 2014{\natexlab{a}}, \mnras, 440, 2944

\bibitem[{{Kaviraj}(2014{\natexlab{b}})}]{kaviraj2014a}
---. 2014{\natexlab{b}}, \mnras, 437, L41

\bibitem[{{Kaviraj} {et~al.}(2015){Kaviraj}, {Devriendt}, {Dubois}, {Slyz},
  {Welker}, {Pichon}, {Peirani}, \& {Le Borgne}}]{kaviraj2015a}
{Kaviraj}, S., {Devriendt}, J., {Dubois}, Y., {Slyz}, A., {Welker}, C.,
  {Pichon}, C., {Peirani}, S., \& {Le Borgne}, D. 2015, \mnras, 452, 2845

\bibitem[{{Kaviraj} {et~al.}(2005){Kaviraj}, {Devriendt}, {Ferreras}, \&
  {Yi}}]{kaviraj2005a}
{Kaviraj}, S., {Devriendt}, J.~E.~G., {Ferreras}, I., \& {Yi}, S.~K. 2005,
  \mnras, 360, 60

\bibitem[{{Kaviraj} {et~al.}(2017){Kaviraj}, {Laigle}, {Kimm}, {Devriendt},
  {Dubois}, {Pichon}, {Slyz}, {Chisari}, \& {Peirani}}]{kaviraj2017a}
{Kaviraj}, S., {et~al.} 2017, \mnras, 467, 4739

\bibitem[{{Kaviraj} {et~al.}(2009){Kaviraj}, {Peirani}, {Khochfar}, {Silk}, \&
  {Kay}}]{kaviraj2009a}
{Kaviraj}, S., {Peirani}, S., {Khochfar}, S., {Silk}, J., \& {Kay}, S. 2009,
  \mnras, 394, 1713

\bibitem[{{Koekemoer} {et~al.}(2011){Koekemoer}, {Faber}, {Ferguson}, {Grogin},
  {Kocevski}, {Koo}, {Lai}, {Lotz}, {Lucas}, {McGrath}, {Ogaz}, {Rajan},
  {Riess}, {Rodney}, {Strolger}, {Casertano}, {Castellano}, {Dahlen},
  {Dickinson}, {Dolch}, {Fontana}, {Giavalisco}, {Grazian}, {Guo}, {Hathi},
  {Huang}, {van der Wel}, {Yan}, {Acquaviva}, {Alexander}, {Almaini}, {Ashby},
  {Barden}, {Bell}, {Bournaud}, {Brown}, {Caputi}, {Cassata}, {Challis},
  {Chary}, {Cheung}, {Cirasuolo}, {Conselice}, {Roshan Cooray}, {Croton},
  {Daddi}, {Dav{\'e}}, {de Mello}, {de Ravel}, {Dekel}, {Donley}, {Dunlop},
  {Dutton}, {Elbaz}, {Fazio}, {Filippenko}, {Finkelstein}, {Frazer}, {Gardner},
  {Garnavich}, {Gawiser}, {Gruetzbauch}, {Hartley}, {H{\"a}ussler},
  {Herrington}, {Hopkins}, {Huang}, {Jha}, {Johnson}, {Kartaltepe},
  {Khostovan}, {Kirshner}, {Lani}, {Lee}, {Li}, {Madau}, {McCarthy},
  {McIntosh}, {McLure}, {McPartland}, {Mobasher}, {Moreira}, {Mortlock},
  {Moustakas}, {Mozena}, {Nandra}, {Newman}, {Nielsen}, {Niemi}, {Noeske},
  {Papovich}, {Pentericci}, {Pope}, {Primack}, {Ravindranath}, {Reddy},
  {Renzini}, {Rix}, {Robaina}, {Rosario}, {Rosati}, {Salimbeni}, {Scarlata},
  {Siana}, {Simard}, {Smidt}, {Snyder}, {Somerville}, {Spinrad}, {Straughn},
  {Telford}, {Teplitz}, {Trump}, {Vargas}, {Villforth}, {Wagner}, {Wandro},
  {Wechsler}, {Weiner}, {Wiklind}, {Wild}, {Wilson}, {Wuyts}, \&
  {Yun}}]{koekemoer2011a}
{Koekemoer}, A.~M., {et~al.} 2011, \apjs, 197, 36

\bibitem[{{Leauthaud} {et~al.}(2012){Leauthaud}, {Tinker}, {Bundy}, {Behroozi},
  {Massey}, {Rhodes}, {George}, {Kneib}, {Benson}, {Wechsler}, {Busha},
  {Capak}, {Cort{\^e}s}, {Ilbert}, {Koekemoer}, {Le F{\`e}vre}, {Lilly},
  {McCracken}, {Salvato}, {Schrabback}, {Scoville}, {Smith}, \&
  {Taylor}}]{leauthaud2012a}
{Leauthaud}, A., {et~al.} 2012, \apj, 744, 159

\bibitem[{{Lin} {et~al.}(2008){Lin}, {Patton}, {Koo}, {Casteels}, {Conselice},
  {Faber}, {Lotz}, {Willmer}, {Hsieh}, {Chiueh}, {Newman}, {Novak}, {Weiner},
  \& {Cooper}}]{lin2008a}
{Lin}, L., {et~al.} 2008, \apj, 681, 232

\bibitem[{{Liske} {et~al.}(2015){Liske}, {Baldry}, {Driver}, {Tuffs},
  {Alpaslan}, {Andrae}, {Brough}, {Cluver}, {Grootes}, {Gunawardhana},
  {Kelvin}, {Loveday}, {Robotham}, {Taylor}, {Bamford}, {Bland-Hawthorn},
  {Brown}, {Drinkwater}, {Hopkins}, {Meyer}, {Norberg}, {Peacock}, {Agius},
  {Andrews}, {Bauer}, {Ching}, {Colless}, {Conselice}, {Croom}, {Davies}, {De
  Propris}, {Dunne}, {Eardley}, {Ellis}, {Foster}, {Frenk}, {H{\"a}u{\ss}ler},
  {Holwerda}, {Howlett}, {Ibarra}, {Jarvis}, {Jones}, {Kafle}, {Lacey},
  {Lange}, {Lara-L{\'o}pez}, {L{\'o}pez-S{\'a}nchez}, {Maddox}, {Madore},
  {McNaught-Roberts}, {Moffett}, {Nichol}, {Owers}, {Palamara}, {Penny},
  {Phillipps}, {Pimbblet}, {Popescu}, {Prescott}, {Proctor}, {Sadler},
  {Sansom}, {Seibert}, {Sharp}, {Sutherland}, {V{\'a}zquez-Mata}, {van Kampen},
  {Wilkins}, {Williams}, \& {Wright}}]{liske2015a}
{Liske}, J., {et~al.} 2015, \mnras, 452, 2087

\bibitem[{{Lofthouse} {et~al.}(2017){Lofthouse}, {Kaviraj}, {Conselice},
  {Mortlock}, \& {Hartley}}]{lofthouse2017a}
{Lofthouse}, E.~K., {Kaviraj}, S., {Conselice}, C.~J., {Mortlock}, A., \&
  {Hartley}, W. 2017, \mnras, 465, 2895

\bibitem[{{Lotz} {et~al.}(2008){Lotz}, {Davis}, {Faber}, {Guhathakurta},
  {Gwyn}, {Huang}, {Koo}, {Le Floc'h}, {Lin}, {Newman}, {Noeske}, {Papovich},
  {Willmer}, {Coil}, {Conselice}, {Cooper}, {Hopkins}, {Metevier}, {Primack},
  {Rieke}, \& {Weiner}}]{lotz2008a}
{Lotz}, J.~M., {et~al.} 2008, \apj, 672, 177

\bibitem[{{Lotz} {et~al.}(2004){Lotz}, {Primack}, \& {Madau}}]{lotz2004a}
{Lotz}, J.~M., {Primack}, J., \& {Madau}, P. 2004, \aj, 128, 163

\bibitem[{{LSST Dark Energy Science Collaboration}(2012)}]{LSSTDESC}
{LSST Dark Energy Science Collaboration}. 2012, arXiv:1211.0310

\bibitem[{{LSST Science Collaboration} {et~al.}(2009){LSST Science
  Collaboration}, {Abell}, {Allison}, {Anderson}, {Andrew}, {Angel}, {Armus},
  {Arnett}, {Asztalos}, {Axelrod}, \& et~al.}]{LSSTSciBook}
{LSST Science Collaboration}, {et~al.} 2009, arXiv:0912.0201

\bibitem[{{Madau} \& {Dickinson}(2014)}]{madau2014a}
{Madau}, P., \& {Dickinson}, M. 2014, \araa, 52, 415

\bibitem[{{Maddox} {et~al.}(2016){Maddox}, {Jarvis}, \&
  {Oosterloo}}]{maddox2016a}
{Maddox}, N., {Jarvis}, M.~J., \& {Oosterloo}, T.~A. 2016, \mnras, 460, 3419

\bibitem[{{Mart{\'{\i}}nez-Delgado} {et~al.}(2008){Mart{\'{\i}}nez-Delgado},
  {Pe{\~n}arrubia}, {Gabany}, {Trujillo}, {Majewski}, \&
  {Pohlen}}]{martinez-delgado2008a}
{Mart{\'{\i}}nez-Delgado}, D., {Pe{\~n}arrubia}, J., {Gabany}, R.~J.,
  {Trujillo}, I., {Majewski}, S.~R., \& {Pohlen}, M. 2008, \apj, 689, 184

\bibitem[{{Mauduit} {et~al.}(2012){Mauduit}, {Lacy}, {Farrah}, {Surace},
  {Jarvis}, {Oliver}, {Maraston}, {Vaccari}, {Marchetti}, {Zeimann},
  {Gonz{\'a}les-Solares}, {Pforr}, {Petric}, {Henriques}, {Thomas}, {Afonso},
  {Rettura}, {Wilson}, {Falder}, {Geach}, {Huynh}, {Norris}, {Seymour},
  {Richards}, {Stanford}, {Alexander}, {Becker}, {Best}, {Bizzocchi},
  {Bonfield}, {Castro}, {Cava}, {Chapman}, {Christopher}, {Clements}, {Covone},
  {Dubois}, {Dunlop}, {Dyke}, {Edge}, {Ferguson}, {Foucaud}, {Franceschini},
  {Gal}, {Grant}, {Grossi}, {Hatziminaoglou}, {Hickey}, {Hodge}, {Huang},
  {Ivison}, {Kim}, {LeFevre}, {Lehnert}, {Lonsdale}, {Lubin}, {McLure},
  {Messias}, {Mart{\'{\i}}nez-Sansigre}, {Mortier}, {Nielsen}, {Ouchi},
  {Parish}, {Perez-Fournon}, {Pierre}, {Rawlings}, {Readhead}, {Ridgway},
  {Rigopoulou}, {Romer}, {Rosebloom}, {Rottgering}, {Rowan-Robinson}, {Sajina},
  {Simpson}, {Smail}, {Squires}, {Stevens}, {Taylor}, {Trichas}, {Urrutia},
  {van Kampen}, {Verma}, \& {Xu}}]{mauduit2012a}
{Mauduit}, J.-C., {et~al.} 2012, \pasp, 124, 714

\bibitem[{{McGaugh} {et~al.}(2000){McGaugh}, {Schombert}, {Bothun}, \& {de
  Blok}}]{mcgaugh2000a}
{McGaugh}, S.~S., {Schombert}, J.~M., {Bothun}, G.~D., \& {de Blok}, W.~J.~G.
  2000, \apjl, 533, L99

\bibitem[{{Meyer} {et~al.}(2015){Meyer}, {Robotham}, {Obreschkow}, {Driver},
  {Staveley-Smith}, \& {Zwaan}}]{meyer2015a}
{Meyer}, M., {Robotham}, A., {Obreschkow}, D., {Driver}, S., {Staveley-Smith},
  L., \& {Zwaan}, M. 2015, arXiv:1501.01082

\bibitem[{{Meyer} {et~al.}(2016){Meyer}, {Meyer}, {Obreschkow}, \&
  {Staveley-Smith}}]{meyer2016a}
{Meyer}, S.~A., {Meyer}, M., {Obreschkow}, D., \& {Staveley-Smith}, L. 2016,
  \mnras, 455, 3136

\bibitem[{{Miyazaki} {et~al.}(2012){Miyazaki}, {Komiyama}, {Nakaya}, {Kamata},
  {Doi}, {Hamana}, {Karoji}, {Furusawa}, {Kawanomoto}, {Morokuma}, {Ishizuka},
  {Nariai}, {Tanaka}, {Uraguchi}, {Utsumi}, {Obuchi}, {Okura}, {Oguri},
  {Takata}, {Tomono}, {Kurakami}, {Namikawa}, {Usuda}, {Yamanoi}, {Terai},
  {Uekiyo}, {Yamada}, {Koike}, {Aihara}, {Fujimori}, {Mineo}, {Miyatake},
  {Yasuda}, {Nishizawa}, {Saito}, {Tanaka}, {Uchida}, {Katayama}, {Wang},
  {Chen}, {Lupton}, {Loomis}, {Bickerton}, {Price}, {Gunn}, {Suzuki},
  {Miyazaki}, {Muramatsu}, {Yamamoto}, {Endo}, {Ezaki}, {Itoh}, {Miwa},
  {Yokota}, {Matsuda}, {Ebinuma}, \& {Takeshi}}]{miyazaki2012a}
{Miyazaki}, S., {et~al.} 2012, in Society of Photo-Optical Instrumentation
  Engineers (SPIE) Conference Series, Vol. 8446, Society of Photo-Optical
  Instrumentation Engineers (SPIE) Conference Series, 0

\bibitem[{{National Research Council}(2010)}]{nrc2010a}
{National Research Council}. 2010, New Worlds, New Horizons in Astronomy and
  Astrophysics (Washington, DC: The National Academies Press)

\bibitem[{{Newman}(2008)}]{newman2008a}
{Newman}, J.~A. 2008, \apj, 684, 88

\bibitem[{{Newman} {et~al.}(2015){Newman}, {Abate}, {Abdalla}, {Allam},
  {Allen}, {Ansari}, {Bailey}, {Barkhouse}, {Beers}, {Blanton}, {Brodwin},
  {Brownstein}, {Brunner}, {Carrasco Kind}, {Cervantes-Cota}, {Cheu},
  {Chisari}, {Colless}, {Comparat}, {Coupon}, {Cunha}, {de la Macorra},
  {Dell'Antonio}, {Frye}, {Gawiser}, {Gehrels}, {Grady}, {Hagen}, {Hall},
  {Hearin}, {Hildebrandt}, {Hirata}, {Ho}, {Honscheid}, {Huterer},
  {Ivezi{\'c}}, {Kneib}, {Kruk}, {Lahav}, {Mandelbaum}, {Marshall}, {Matthews},
  {M{\'e}nard}, {Miquel}, {Moniez}, {Moos}, {Moustakas}, {Myers}, {Papovich},
  {Peacock}, {Park}, {Rahman}, {Rhodes}, {Ricol}, {Sadeh}, {Slozar}, {Schmidt},
  {Stern}, {Anthony Tyson}, {von der Linden}, {Wechsler}, {Wood-Vasey}, \&
  {Zentner}}]{newman2015a}
{Newman}, J.~A., {et~al.} 2015, Astroparticle Physics, 63, 81

\bibitem[{{Noeske} {et~al.}(2007){Noeske}, {Weiner}, {Faber}, {Papovich},
  {Koo}, {Somerville}, {Bundy}, {Conselice}, {Newman}, {Schiminovich}, {Le
  Floc'h}, {Coil}, {Rieke}, {Lotz}, {Primack}, {Barmby}, {Cooper}, {Davis},
  {Ellis}, {Fazio}, {Guhathakurta}, {Huang}, {Kassin}, {Martin}, {Phillips},
  {Rich}, {Small}, {Willmer}, \& {Wilson}}]{noeske2007a}
{Noeske}, K.~G., {et~al.} 2007, \apjl, 660, L43

\bibitem[{{Oh} {et~al.}(2015){Oh}, {Hunter}, {Brinks}, {Elmegreen}, {Schruba},
  {Walter}, {Rupen}, {Young}, {Simpson}, {Johnson}, {Herrmann}, {Ficut-Vicas},
  {Cigan}, {Heesen}, {Ashley}, \& {Zhang}}]{oh2015a}
{Oh}, S.-H., {et~al.} 2015, arXiv:1502.01281

\bibitem[{{Okabe} \& {Smith}(2016)}]{okabe2016a}
{Okabe}, N., \& {Smith}, G.~P. 2016, \mnras, 461, 3794

\bibitem[{{Okabe} {et~al.}(2013){Okabe}, {Smith}, {Umetsu}, {Takada}, \&
  {Futamase}}]{okabe2013a}
{Okabe}, N., {Smith}, G.~P., {Umetsu}, K., {Takada}, M., \& {Futamase}, T.
  2013, \apjl, 769, L35

\bibitem[{{Pasquali} {et~al.}(2010){Pasquali}, {Gallazzi}, {Fontanot}, {van den
  Bosch}, {De Lucia}, {Mo}, \& {Yang}}]{pasquali2010a}
{Pasquali}, A., {Gallazzi}, A., {Fontanot}, F., {van den Bosch}, F.~C., {De
  Lucia}, G., {Mo}, H.~J., \& {Yang}, X. 2010, \mnras, 407, 937

\bibitem[{{Ponomareva} {et~al.}(2016){Ponomareva}, {Verheijen}, \&
  {Bosma}}]{ponomareva2016a}
{Ponomareva}, A.~A., {Verheijen}, M.~A.~W., \& {Bosma}, A. 2016,
  arXiv:1609.00378

\bibitem[{{Richards} {et~al.}(2006){Richards}, {Lacy}, {Storrie-Lombardi},
  {Hall}, {Gallagher}, {Hines}, {Fan}, {Papovich}, {Vanden Berk}, {Trammell},
  {Schneider}, {Vestergaard}, {York}, {Jester}, {Anderson}, {Budav{\'a}ri}, \&
  {Szalay}}]{richards2006a}
{Richards}, G.~T., {et~al.} 2006, \apjs, 166, 470

\bibitem[{{Robertson} {et~al.}(2007){Robertson}, {Li}, {Cox}, {Hernquist}, \&
  {Hopkins}}]{robertson2007a}
{Robertson}, B., {Li}, Y., {Cox}, T.~J., {Hernquist}, L., \& {Hopkins}, P.~F.
  2007, \apj, 667, 60

\bibitem[{{Robotham} {et~al.}(2014){Robotham}, {Driver}, {Davies}, {Hopkins},
  {Baldry}, {Agius}, {Bauer}, {Bland-Hawthorn}, {Brough}, {Brown}, {Cluver},
  {De Propris}, {Drinkwater}, {Holwerda}, {Kelvin}, {Lara-Lopez}, {Liske},
  {L{\'o}pez-S{\'a}nchez}, {Loveday}, {Mahajan}, {McNaught-Roberts}, {Moffett},
  {Norberg}, {Obreschkow}, {Owers}, {Penny}, {Pimbblet}, {Prescott}, {Taylor},
  {van Kampen}, \& {Wilkins}}]{robotham2014a}
{Robotham}, A.~S.~G., {et~al.} 2014, \mnras, 444, 3986

\bibitem[{{Rykoff} {et~al.}(2014){Rykoff}, {Rozo}, {Busha}, {Cunha},
  {Finoguenov}, {Evrard}, {Hao}, {Koester}, {Leauthaud}, {Nord}, {Pierre},
  {Reddick}, {Sadibekova}, {Sheldon}, \& {Wechsler}}]{rykoff2014a}
{Rykoff}, E.~S., {et~al.} 2014, \apj, 785, 104

\bibitem[{{Salim} {et~al.}(2016){Salim}, {Lee}, {Janowiecki}, {da Cunha},
  {Dickinson}, {Boquien}, {Burgarella}, {Salzer}, \& {Charlot}}]{salim2016a}
{Salim}, S., {et~al.} 2016, \apjs, 227, 2

\bibitem[{{Sersic}(1968)}]{sersic1968a}
{Sersic}, J.~L. 1968, {Atlas de galaxias australes.} (Cordoba, Argentina:
  Observatorio Astronomico)

\bibitem[{{Stott} {et~al.}(2012){Stott}, {Hickox}, {Edge}, {Collins}, {Hilton},
  {Harrison}, {Romer}, {Rooney}, {Kay}, {Miller}, {Sahl{\'e}n}, {Lloyd-Davies},
  {Mehrtens}, {Hoyle}, {Liddle}, {Viana}, {McCarthy}, {Schaye}, \&
  {Booth}}]{stott2012a}
{Stott}, J.~P., {et~al.} 2012, \mnras, 422, 2213

\bibitem[{{Tiley} {et~al.}(2016{\natexlab{a}}){Tiley}, {Bureau}, {Saintonge},
  {Topal}, {Davis}, \& {Torii}}]{tiley2016b}
{Tiley}, A.~L., {Bureau}, M., {Saintonge}, A., {Topal}, S., {Davis}, T.~A., \&
  {Torii}, K. 2016{\natexlab{a}}, \mnras, 461, 3494

\bibitem[{{Tiley} {et~al.}(2016{\natexlab{b}}){Tiley}, {Stott}, {Swinbank},
  {Bureau}, {Harrison}, {Bower}, {Johnson}, {Bunker}, {Jarvis}, {Magdis},
  {Sharples}, {Smail}, {Sobral}, \& {Best}}]{tiley2016a}
{Tiley}, A.~L., {et~al.} 2016{\natexlab{b}}, \mnras, 460, 103

\bibitem[{{Trachternach} {et~al.}(2008){Trachternach}, {de Blok}, {Walter},
  {Brinks}, \& {Kennicutt}}]{trachternach2008a}
{Trachternach}, C., {de Blok}, W.~J.~G., {Walter}, F., {Brinks}, E., \&
  {Kennicutt}, R.~C. 2008, \aj, 136, 2720

\bibitem[{{Tully} \& {Fisher}(1977)}]{tully1977a}
{Tully}, R.~B., \& {Fisher}, J.~R. 1977, \aap, 54, 661

\bibitem[{{van Dokkum} {et~al.}(2014){van Dokkum}, {Abraham}, \&
  {Merritt}}]{van_dokkum2014a}
{van Dokkum}, P.~G., {Abraham}, R., \& {Merritt}, A. 2014, \apjl, 782, L24

\bibitem[{{Verheijen} {et~al.}(2010){Verheijen}, {Deshev}, {van Gorkom},
  {Poggianti}, {Chung}, {Cybulski}, {Dwarakanath}, {Montero-Castano},
  {Morrison}, {Schiminovich}, {Szomoru}, \& {Yun}}]{verheijen2010a}
{Verheijen}, M., {et~al.} 2010, arXiv:1009.0279

\bibitem[{{Verheijen}(2001)}]{verheijen2001a}
{Verheijen}, M.~A.~W. 2001, \apj, 563, 694

\bibitem[{{Wang} {et~al.}(2016){Wang}, {Mo}, {Yang}, {Zhang}, {Shi}, {Jing},
  {Liu}, {Li}, {Kang}, \& {Gao}}]{wang2016a}
{Wang}, H., {et~al.} 2016, \apj, 831, 164

\bibitem[{{Weiner} {et~al.}(2006){Weiner}, {Willmer}, {Faber}, {Harker},
  {Kassin}, {Phillips}, {Melbourne}, {Metevier}, {Vogt}, \&
  {Koo}}]{weiner2006a}
{Weiner}, B.~J., {et~al.} 2006, \apj, 653, 1049

\bibitem[{{Willott} {et~al.}(2013){Willott}, {McLure}, {Hibon}, {Bielby},
  {McCracken}, {Kneib}, {Ilbert}, {Bonfield}, {Bruce}, \&
  {Jarvis}}]{willott2013a}
{Willott}, C.~J., {et~al.} 2013, \aj, 145, 4

\bibitem[{{York} {et~al.}(2000){York}, {Adelman}, {Anderson}, {Anderson},
  {Annis}, {Bahcall}, {Bakken}, {Barkhouser}, {Bastian}, {Berman}, {Boroski},
  {Bracker}, {Briegel}, {Briggs}, {Brinkmann}, {Brunner}, {Burles}, {Carey},
  {Carr}, {Castander}, {Chen}, {Colestock}, {Connolly}, {Crocker}, {Csabai},
  {Czarapata}, {Davis}, {Doi}, {Dombeck}, {Eisenstein}, {Ellman}, {Elms},
  {Evans}, {Fan}, {Federwitz}, {Fiscelli}, {Friedman}, {Frieman}, {Fukugita},
  {Gillespie}, {Gunn}, {Gurbani}, {de Haas}, {Haldeman}, {Harris}, {Hayes},
  {Heckman}, {Hennessy}, {Hindsley}, {Holm}, {Holmgren}, {Huang}, {Hull},
  {Husby}, {Ichikawa}, {Ichikawa}, {Ivezi{\'c}}, {Kent}, {Kim}, {Kinney},
  {Klaene}, {Kleinman}, {Kleinman}, {Knapp}, {Korienek}, {Kron}, {Kunszt},
  {Lamb}, {Lee}, {Leger}, {Limmongkol}, {Lindenmeyer}, {Long}, {Loomis},
  {Loveday}, {Lucinio}, {Lupton}, {MacKinnon}, {Mannery}, {Mantsch}, {Margon},
  {McGehee}, {McKay}, {Meiksin}, {Merelli}, {Monet}, {Munn}, {Narayanan},
  {Nash}, {Neilsen}, {Neswold}, {Newberg}, {Nichol}, {Nicinski}, {Nonino},
  {Okada}, {Okamura}, {Ostriker}, {Owen}, {Pauls}, {Peoples}, {Peterson},
  {Petravick}, {Pier}, {Pope}, {Pordes}, {Prosapio}, {Rechenmacher}, {Quinn},
  {Richards}, {Richmond}, {Rivetta}, {Rockosi}, {Ruthmansdorfer}, {Sandford},
  {Schlegel}, {Schneider}, {Sekiguchi}, {Sergey}, {Shimasaku}, {Siegmund},
  {Smee}, {Smith}, {Snedden}, {Stone}, {Stoughton}, {Strauss}, {Stubbs},
  {SubbaRao}, {Szalay}, {Szapudi}, {Szokoly}, {Thakar}, {Tremonti}, {Tucker},
  {Uomoto}, {Vanden Berk}, {Vogeley}, {Waddell}, {Wang}, {Watanabe},
  {Weinberg}, {Yanny}, {Yasuda}, \& {SDSS Collaboration}}]{york2000a}
{York}, D.~G., {et~al.} 2000, \aj, 120, 1579

\end{thebibliography}

%---END---
\end{document}


